% CREATED BY DAVID FRISK, 2018
\thispagestyle{plain}			% Supress header
\section*{Acknowledgements}
We would like to sincerely thank the Powertrain Engineering department at Volvo Group Trucks and Technology, for giving the opportunity to conduct this case study at their organization. Also, this work was conducted in collaboration with the Industrial Economy department at Chalmers University of technology.
\\
\\
We are greatly indebted to our supervisors at Volvo, Sören Hansen and Jonna Nygren for their continuous support, providing us direction with collecting the data, getting us in contact with the right people and similar needs. This also helped us channel our focus and scope the problem effectively.
\\
\\
From the academic perspective, we received guidance from Prof. Mats Winroth, Program Director for Master in Quality and Operations Management. He was the supervisor and examiner for this thesis from Chalmers University. He provided us knowledge about various literatures, frameworks and books that could help us connect the empirical findings with the literature facts and in end draw conclusions.
\\
\\
A Special thanks Mats Leijon, from Volvo Construction Equipment for evaluating us from time to time and providing different directions to think and structure this thesis work. This helped us use various frameworks and think from a holistic perspective.
\\
\\
As a part of this thesis, various interviews were conducted and we would like to thank all the interviewees for their time and valuable inputs. 
\\
\\
A survey was also conducted where around twenty percent of the total employees in PE departments responded. This gave us more insights for conducting the thesis work, every response was valuable hence we would like to thank each employee for their inputs.   


\vspace{1.5cm}
\hfill
Deepak Balihalli, Nikhita Bhushi, Gothenburg, June 2019

\newpage				% Create empty back of side
\thispagestyle{empty}
\mbox{}