\chapter{Ethics}

This chapter evokes the ethical concerns taken during this master thesis. Initially the steps taken to establish trustworthiness of the study is detailed. The last part describes all the ethical considerations taken while performing various research methods and analysis.

\section{Trustworthiness}
According to Bryman and Bell (2015), there are four criteria to ensure trustworthiness for a qualitative study and these are credibility, transferability, dependability, and confirmability. \\ 

To ensure credibility of the findings various measures are employed. Thorough literature study is done previously to ensure good practice before conducting interviews and the survey. Each of the interviews are recorded so as to compare and verify the transcription done of the interview. In case of further doubts, the interviewee is contacted for clarifications. For the survey, the pilot test and discussion with supervisors ensured that the points mentioned in the survey are in the scope for the thesis. As the respondents had sufficient time to reply to the survey (3 weeks) and it was comprised of simple questions which was improved after the pilot test, the resulting findings from both research methods are credible. Inturn, they also act as triangulation of facts as the input is taken from employees, managers, directors and vice-president.\\

As it is a single case study transferability is reduced. But, the resulting analysis can still be transferred easily to other global sites of Volvo - Powertrain engineering with little or no changes. The insights of improving the effectiveness of KPIs can be useful to other verticals of Volvo group such as complete vehicle, purchasing etc. as they are part of the same Volvo culture with supporting mechanisms being similar. Academically, some findings can be applied to multinational firms with large product development teams to increase the efficacy of KPI management.\\

To ensure dependability of data over the course of thesis, triangulation of data received from interviews and surveys which are done at different phases can prove to be one option. The transcripts of interviews and survey is coded twice, once by each of thesis students to ensure consistency of findings. External audit was not possible as the research deals with some confidential details.\\

As both of thesis students were not part of Volvo, this brings in the confirmability as it is analysed through the perspective of third person. The interview insights, data from Volvo website, survey findings etc. are reported by keeping maximum objectivity in mind. Although it is impossible to be utterly objective, the research has been conducted completely in good faith.\\

\section{Ethical considerations}
During the course of the thesis,various ethical considerations have been taken. The  four main areas concerning ethical principles are: participant harm, lack of informed consent, privacy invasion and deception (Diener & Crandall,1978). All of these principles are kept in mind throughout the duration of the thesis.\\

The interviews were conducted after informing the interviewees about the intention of questions and how the data will be handled. The duration of the interview was clearly mentioned priorly and was adhered, thus negating any chance of deception and lack of informed consent.Interviewees had option to not answer if they thought it would bring any harm upon them. The resulting transcripts and audio records are safely guarded and not shared with any personnel ensuring no participant harm.\\


The survey was sent out with clear description about the need, the format, appropriate amount of time taken to complete and data usage rules. As there was no personal demographic data collected in the survey and no emails collected from the replies, there was complete privacy of the respondents. The survey was verified by the top management and sent out through official PE-Sweden communication channels to bring in more credibility. The information uncovered from the survey was only accessible to both the research students ensuring complete protection.\\

Concerns regarding Data protection, reciprocity and trust were also considered. All the interview and survey data was stored safely in company provided laptops. The cloud data storage was verified to be GDPR compliant. Reciprocity and trust between researchers and respondents was the base for the whole thesis. Both acknowledged the advantages of participation and helped each other.\\

%Overall, all the ethical considerations were taken care.